Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Adding the tables.

@@

>>>>

\begin{figure}[t]
\begin{center}
\begin{center}
	\begin{tabular}{|l|l|}
	\hline
	\multicolumn{2}{|c|}{\bf Testing Data Set} \\ \hline
	{\bf Label} & {\bf Count}  \\ \hline
	test & 17237 \\ \hline
	none & 202438 \\ \hline
	 problem & 30276 \\ \hline
	 treatment & 17298 \\ \hline
	\end{tabular}
\end{center}

\begin{center}
	\begin{tabular}{|l|l|}
	\hline
	\multicolumn{2}{|c|}{\bf Training Data Set} \\ \hline
	{\bf Label} & {\bf Count}  \\ \hline
	test & 8492 \\ \hline
	none & 114783 \\ \hline
	 problem & 17326 \\ \hline
	 treatment & 8940 \\ \hline
	\end{tabular}
\end{center}
\end{center}
\caption{The number of each class the in testing and training data sets.}
\label{fig:data_set_counts}
\end{figure}

@@

	\begin{tabular}{|l|l|l|}
	\hline
	{\bf Feature Set} & {\bf Classifier} & {\bf F1 Score}  \\ \hline

	\end{tabular}
